White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2017-09-14 papers/wdmerger_II/paper.tex
Correct the data on what ODE tolerances we use

In our \microphysics\ repository we provide several software options for
solving a set of coupled stiff ODEs. For this work our primary integrator
is the classic \vode\ integrator \citep{vode}, of which we have a version
compatible with our software interfaces in the \microphysics\ repository.
We also employ an implementation of the well known variable-order Richardson
extrapolation method presented by \citet{stoer:1980}, that is similar to the
integrator which ships with the original versions of the networks mentioned
above. Our experience shows that relying on a single ODE integrator for the
variety of stiff ODEs that are present in a collision is insufficient, as we
sometimes run into integration failures. A combination of the two integrators
is usually sufficient, however: we first try \vode, and if that fails, we then
try the Stoer and Bulirsch method. Since it is possible for neither method to
succeed, we have one more backup scheme. Our specified error tolerances are
$10^{-6}$ for the energy and temperature ODEs, and $10^{-8}$ for the
nuclear abundance ODEs (we discuss the sensitivity to this choice in
\autoref{sec:parameters:tolerance}). We can loosen these tolerances in an
attempt to give the integrator an easier time. If both \vode\ and the Stoer
and Bulirsch algorithm fail, then we loosen the tolerances by a multiplicative
factor of 25\%, and then repeat the attempts with \vode\ and Stoer and Bulirsch.
We keep doing this until either we have loosened the tolerances enough for one
of the two methods to succeed, or until we have loosened the tolerances by two
orders of magnitude, at which point we finally give up. We have found that this
scheme is resilient enough to handle all of the simulations shown below.

>>>>

In our \microphysics\ repository we provide several software options for
solving a set of coupled stiff ODEs. For this work our primary integrator
is the classic \vode\ integrator \citep{vode}, of which we have a version
compatible with our software interfaces in the \microphysics\ repository.
We also employ an implementation of the well known variable-order Richardson
extrapolation method presented by \citet{stoer:1980}, that is similar to the
integrator which ships with the original versions of the networks mentioned
above. Our experience shows that relying on a single ODE integrator for the
variety of stiff ODEs that are present in a collision is insufficient, as we
sometimes run into integration failures. A combination of the two integrators
is usually sufficient, however: we first try \vode, and if that fails, we then
try the Stoer and Bulirsch method. Since it is possible for neither method to
succeed, we have one more backup scheme. Our specified (relative and absolute)
error tolerances are uniformly $10^{-6}$ for the energy, temperature, and nuclear
abundance ODEs (we discuss the sensitivity to this choice in
\autoref{sec:parameters:tolerance}). We can loosen these tolerances in an
attempt to give the integrator an easier time. If both \vode\ and the Stoer
and Bulirsch algorithm fail, then we loosen the tolerances by a multiplicative
factor of 25\%, and then repeat the attempts with \vode\ and Stoer and Bulirsch.
We keep doing this until either we have loosened the tolerances enough for one
of the two methods to succeed, or until we have loosened the tolerances by two
orders of magnitude, at which point we finally give up. We have found that this
scheme is resilient enough to handle all of the simulations shown below.
